---
title: "pseudocode"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Gaudi

## Spec

We could go with an idea very similar to `ggplot2`'s, with `channel`s replacing `geom`s but with similar characteristics. We could have aesthetics in both the main object (represented by a call to `gaudi`) and in the individual channels. On top of that we would offer additional methods (like `theme_blank` and `facet_wrap` in `ggplot2`).

Ideas for _channels_:

- instruments (piano, marimba, KORG MB-88, etc.)
- beats (drums, plops, etc.)
- noise
- sine

Ideas for _aesthetics_:

- key
- progression
- harmony
- amplitude
- height (C1, C2, C3 etc)
- notes
- style (staccato, legato, etc.)
- noise/randomness
- distortion
- fade
 
Ideas for _additional methods_:

- Setting (echoes, balance, Dolby surround etc.)
- Equalizer


## Pseudocode

```{r, eval = FALSE}
worldbank_data %>% 
  gaudi(time = year) %>% 
  channel_piano(chord = value, key = country, progression = year, noise = noise_jitter(seed = value)) %>%
  channel_beat(frame = "4/4", noise = noise_triolic(seed = 1)) %>%
  setting(room = "Dolby surround")
```

